# tdcstyle

Is a styler which makes data.table syntax in particular nicer. Here's some example of desirable style:

```{r}
  donors[
    is.na(remove_dm1)
    & is.na(remove_dm2),
    .N,
    keyby = pack]

  donors[
    is.na(remove_dm1)
    & is.na(remove_dm2),
    let(new_var = "test",
        new_var2 = "test2")]

  donors[,
    let(new_var = "test")]
```


## Using {styler}

Presumably the styler will be built on the [{styler}](https://styler.r-lib.org/) package.

### Customising Styler

```{r}
  library(magrittr)
  library(styler)
  library(dplyr)

  is_dt_expr <- function(pd_flat) {
    all(c("'['", "']'") %in% pd_flat$token)
  }

  my_styler <- function(pd_flat) {

    # if open and close [] on same line, do nothing?
    # if comma follows [, remove new lines between
    # if some other expression push it down to newline
    # if filter expression contains & or | at paren level 0, insert a newline before each


    # pull up the last ]
    if(is_dt_expr(pd_flat)) {
      pd_flat$spaces[pd_flat$token_after == "']'"] <- 0
      pd_flat$newlines[pd_flat$token_after == "']'"] <- 0
      pd_flat$lag_newlines[pd_flat$token == "']'"] <- 0
      browser()
    }

    pd_flat
  }

my_style <- function(are_you_sure) {
  create_style_guide(
    space = tibble::lst(my_styler =
    if (are_you_sure) my_styler),
    style_guide_name = "my_style@https://github.com/r-lib/styler",
    style_guide_version = read.dcf(here::here("DESCRIPTION"))[, "Version"]
  )
}

string_to_format <-
"dt[
  is.na(remove_na1),
  ]"


string_to_format_2 <-
'donors[
  is.na(force_reason) & is.na(remove_dm1) & cashemerg_hag_amount >= 1000,
  let(force_include = "Y",
      force_reason = "01. High Mid Value Cash/Emerg",
      pack = "MV"
      )
  ]
'

style_text(string_to_format_2, style = my_style, are_you_sure = TRUE)

styler::style_text(string_to_format_2, style = tidyverse_style)


```
# Questions?

How does styler manage whitespace?

In this code:

```r
donors[
  is.na(force_reason) & is.na(remove_dm1) & cashemerg_hag_amount >= 1000,
  let(force_include = "Y",
      force_reason = "01. High Mid Value Cash/Emerg",
      pack = "MV"
      )
  ]
```

tidyverse_style produces:

```r
donors[
  is.na(force_reason) & is.na(remove_dm1) & cashemerg_hag_amount >= 1000,
  let(
    force_include = "Y",
    force_reason = "01. High Mid Value Cash/Emerg",
    pack = "MV"
  )
]
```

One candidate is: `set_line_break_after_opening_if_call_is_multi_line`

```r
tidyverse_style()$line_break$set_line_break_after_opening_if_call_is_multi_line
styler:::set_line_break_after_opening_if_call_is_multi_line
```

So what happens if we remove this rule?

```r
transformers <- tidyverse_style()
transformers$line_break$set_line_break_after_opening_if_call_is_multi_line <- NULL

styler::style_text(string_to_format_2, transformers = transformers)
```

We get:

```r
donors[
  is.na(force_reason) & is.na(remove_dm1) & cashemerg_hag_amount >= 1000,
  let(force_include = "Y",
    force_reason = "01. High Mid Value Cash/Emerg",
    pack = "MV"
  )
]
```

What indentation rule could be used to fix this?

```r
ls(transformers)
transformers$indention
indent_funs <- transformers$indention
ls(indent_funs)
transformers$indention <- list(
  indent_braces = indent_funs$indent_braces
)

styler::style_text(string_to_format_2, transformers = transformers)
```

Looks like indent_braces is how it works.

```r
debug(styler:::indent_braces)

styler::style_text(string_to_format_2, transformers = transformers)

```

the code for indent_braces:

```r
    indent_indices <- compute_indent_indices(pd, token_opening = c("'('",
        "'['", "'{'"), token_closing = c("')'", "']'", "'}'"))
    pd$indent[indent_indices] <- pd$indent[indent_indices] +
        indent_by
    set_unindention_child(pd, token = "')'", unindent_by = indent_by)

    pd$child
    pd[-indent_indices, ]
    pd
```

So we'll have a hard time creating an indent rule that can work at high and low
level. Because the amount to be indented by under our ideal would be variable,
but the variable is unknown at the level of context where the indentation is
applied.

So I think a sensible approach might be to make a data.table specific styler that assumes code has already been styled by tidyverse?

# Styler working order

from: https://styler.r-lib.org/articles/customizing_styler.html

> The sequence in which styler applies rules on each level of nesting is given in the list below:
>
>    call default_style_guide_attributes() to initialize some variables.
>
>    modify the line breaks (modifying lag_newlines only based on token, token_before, token_after and text).
>
>    modify the spaces (modifying spaces only based on lag_newlines, newlines, multi_line, token, token_before, token_after and text).
>
>    modify the tokens (based on newlines lag_newlines, spaces multi_line, token, token_before, token_after and text).
>
>    modify the indention by changing indention_ref_id (based on newlines lag_newlines, spaces multi_line, token, token_before, token_after and text).




# Example from Dan:

```{r}
library(data.table)
library(lubridate)
library(tdcfun)
library(readxl)
library(mgcv)
library(scales)
library(glue)
library(fst)

charity <- "MSFNZ"

date_dm1 <- as.Date("2022-11-07")
date_dm2 <- as.Date("2022-11-28")
date_nl1 <- as.Date("2022-12-13")

# Import data -------------------------------------------------------------
path <- "../../msf_au/standard_refresh/data"
major_donors <- read_fst(glue("{path}/major_donors.fst"), as.data.table = TRUE)
trans <- read_fst(glue("{path}/trans.fst"), as.data.table = TRUE)
rgtable <- read_fst(glue("{path}/rgtable.fst"), as.data.table = TRUE)
donors <- read_fst(glue("{path}/donors.fst"), as.data.table = TRUE)
exclusions <- read_fst(glue("{path}/exclusions.fst"), as.data.table = TRUE)
suppress_md <- read_fst(glue("{path}/suppress_md.fst"), as.data.table = TRUE)
refresh_date <- readRDS(glue("{path}/refresh_date.Rds"))

dataro_scores <- read_fst(glue("{path}/msf_dataro_dm.fst"), as.data.table = TRUE)
dataro_scores[
  , let(urn = as.character(Constituent.ID),
        score_dm = `Constituent.Specific.Attributes.Dataro.DM.Appeal.Description`,
        rank_dm = `Constituent.Spe.Attributes.Dataro.DM.Appeal.Rank.Description`,
        score_500 = Constituent.Spe.ttributes.Dataro.DM.Appeal...500.Description,
        rank_500 = Constituent.Spe.utes.Dataro.DM.Appeal...500.Rank.Description,
        score_rg = Constituent.Spe..Attributes.Dataro.Convert.to.RG.Description,
        rank_rg = Constituent.Spe.ibutes.Dataro.Convert.to.RG.Rank.Description)]

donors[, `:=`(clean_home = gsub("\\D", "", phone_home),
              clean_work = gsub("\\D", "", phone_work),
              clean_mobile = gsub("\\D", "", phone_mobile))]

add_hag(
  donors = donors,
  trans = trans,
  classification_codes = c(5, 37, 40),
  refresh_date = refresh_date,
  prefix = "cashemerg")

# Apply exclusions --------------------------------------------------------
brief <- last(list.files(
  path = "brief",
  pattern = "data_brief.*xlsx$",
  full.names = TRUE))

## identify current set of exclusions from refresh ----
new_exclusions <- exclusions[
  , .(donor_count = uniqueN(urn)),
  .(group, exclusion_code, description)]

## identify exclusions to be pasted into worksheet ----
dkfunctions::update_exclusions(
  new_exclusions = new_exclusions,
  brief = brief)[] %>%
  copy_data(header = FALSE)

# import data exclusions from spreadsheet ----
appeal_excl <- setDT(read_excel(brief, "Exclusions", skip = 3))

# add exclusion reasons to donor table
targeting_add_wave_removals(donors, exclusions, appeal_excl)

# manual exclusions -------------------------------------------------------
remove_cols <- grep("remove_\\w{3}$", colnames(donors), value = TRUE)

## remove AU donors ----
donors[
  flag_nzdonor == 0,
  (remove_cols) := lapply(.SD, function(x) {
    ifelse(is.na(x), "905-Non New Zealand Address", x)}),
  .SDcols = remove_cols]

## Workplace givers ----
excl_workplace <- trans[classification_code == 30, urn]
donors[
  urn %in% excl_workplace,
  (remove_cols) := lapply(.SD, function(x) {
    ifelse(is.na(x), "990-Workplace Givers", x)}),
  .SDcols = remove_cols]

## cash donors with TM/F2F gifts only ----
tmp_f2fphone <- trans[
  appeal_code %ilike% "NZ"
  & classification_code %in% c(5, 37, 40)
  & channel_code %in% c(3, 10),
  urn]
tmp_other <- trans[
  appeal_code %ilike% "NZ"
  & classification_code %in% c(5, 37, 40)
  & !channel_code %in% c(3, 10),
  urn]
donors[
  urn %in% tmp_f2fphone
  & !urn %in% tmp_other,
  (remove_cols) := lapply(.SD, function(x) {
    ifelse(is.na(x), "991-F2F/Phone only gifts", x)}),
  .SDcols = remove_cols]

## remove RG Active records from DM1/DM2
remove_dm_cols <- grep("remove_dm", colnames(donors), value = TRUE)
donors[
  donor_type == "rg"
  & rg_active_flag == 1,
  (remove_dm_cols) := lapply(.SD, function(x) {
    ifelse(is.na(x), "993-RG Active Donors", x)}),
  .SDcols = remove_dm_cols]


## exclude RTS records ----
tmp_rts <- rbindlist(
  list(
    setDT(read_excel("data/2022 MSF Supporters C5 GNAs_12 Oct 22.xlsx"))[, urn := ID],
    read_excel("data/RTS-NZ_6 October 22.xlsx", col_names = "urn")
  ),
  fill = TRUE)
donors[
  urn %in% tmp_rts$urn,
  (remove_cols) := lapply(.SD, function(x) {
    ifelse(is.na(x), "992-RTS Records", x)}),
  .SDcols = remove_cols]

## exclude manual major donors
tmp_major <- setDT(read_excel("data/20221013 MD NZ SUMMER SUPPRESSIONS.xlsx"))
donors[
  urn %in% tmp_major$`Constituent ID`,
  (remove_cols) := lapply(.SD, function(x) {
    ifelse(is.na(x), "915-Major Donors", x)}),
  .SDcols = remove_cols]

# build exclusion counts for brief ----------------------------------------
exclusion_summary <- targeting_summarise_wave_removals(appeal_excl, donors)
export_cols <- grep("remove_\\w{3}$", colnames(exclusion_summary), value = TRUE)
exclusion_summary[, .SD, .SDcols = export_cols] %>%
  copy_data(header = FALSE, remote = remote)

# Determine inclusions (MAIL) ---------------------------------------------
# NOTE: Update to reflect the contact strategy provided by client.
# Update to separate out NL Mail audiences from NZ audiences

donors[, let(force_include = "N", force_reason = NA_character_, pack = "SV")]

## Cash / Emerg HAG last 2 years > $1,000 - set to mid value ----
donors[
  is.na(force_reason)
  & is.na(remove_dm1)
  & cashemerg_hag_amount >= 1000,
  let(force_include = "Y",
      force_reason = "01. High Mid Value Cash/Emerg",
      pack = "MV")]

## Cash / Emerg HAG last 2 years > $250 - set to mid value ----
donors[
  is.na(force_reason)
  & is.na(remove_dm1)
  & cashemerg_hag_amount >= 250,
  let(force_include = "Y",
      force_reason = "02. Mid Value Cash/Emerg",
      pack = "MV")]

## Any Active RG Only donor with gift is $250-$4000 in the last 2 years ----
tmp_hv_trans <- trans[
  amount >= 200
  & date >= refresh_date %m-% months(24),
  urn]
donors[
  is.na(force_reason)
  & is.na(remove_dm1)
  & donor_type == "rg"
  & urn %in% tmp_hv_trans,
  let(force_include = "Y",
      force_reason = "03. Lapsed RG Only gifts $200-$4,000",
      pack = "MV")]

## dataro_dm ----
donors[
  dataro_scores,
  on = .(urn),
  let(dataro_dm_rank = i.rank_dm,
      dataro_dm_score = i.score_dm,
      dataro_500_score = i.score_500)]
donors[
  is.na(remove_dm1)
  & (dataro_dm_score >= 0.005 | dataro_500_score >= 0.0025),
  let(force_include = "Y",
      force_reason = ifelse(is.na(force_reason), "91. Dataro DM Audience", force_reason),
      targeted_dataro = "Y")]

## Seeds ----
donors[
  segment_code == "Z999"
  & !is.na(addr_line1),
  let(force_include = "Y",
      force_reason = "99. Seeds",
      targeted_tdc = "Y",
      targeted_dataro = "Y")]

# donors[is.na(remove_dm1), .N, k = force_reason]

# Determine inclusions (NEWSLETTER - NZ) -----------------------------------
donors[
  flag_nzdonor == 1,
  let(nl_force = "N",
      nl_group = NA_character_)]

## Active rgcash donors (0-12; cash recency) ----
tmp_group <- donors[
  donor_type == "rgcash"
  & rg_active_flag == 1
  & cash_recency == "0-12",
  urn]
donors[
  is.na(nl_group)
  & is.na(remove_nl1)
  & urn %in% tmp_group,
  let(nl_force = "Y",
      nl_group = "01. Active RG + Cash 0-12")]

## Active rgcash donors (13-24; cash recency) ----
tmp_group <- donors[
  donor_type == "rgcash"
  & rg_active_flag == 1
  & cash_recency == "13-24",
  urn]
donors[
  is.na(nl_group)
  & is.na(remove_nl1)
  & urn %in% tmp_group,
  let(nl_force = "Y",
      nl_group = "02. Active RG + Cash 13-24")]

## active FP ----
tmp_group <- donors[
  rg_active_flag == 1
  & rg_flag == 1,
  urn]
donors[
  is.na(nl_group)
  & is.na(remove_nl1)
  & flag_nzdonor == 1
  & urn %in% tmp_group,
  let(nl_force = "Y",
      nl_group = "03. Active Field Partners")]

## cash donors 0-12 ----
tmp_group <- donors[
  donor_type == "cash"
  & cash_recency %in% c("0-12")
  & flag_nzdonor == 1,
  urn]
donors[
  is.na(nl_group)
  & is.na(remove_nl1)
  & flag_nzdonor == 1
  & urn %in% tmp_group,
  let(nl_force = "Y",
      nl_group = "04. Cash Donors; 0-12")]

## confirmed bequesters ok to mail ----
tmp_group <- exclusions[
  description %in% c("Confirmed", "Re-Confirmed", "Intender", "Enquirer",
                    "Prospect"),
  urn]
donors[
  is.na(nl_group)
  & is.na(remove_nl1)
  & flag_nzdonor == 1
  & urn %in% tmp_group,
  let(nl_force = "Y",
      nl_group = "05. Has Bequest status")]

# seeds
tmp_group <- donors[
  segment_code == "Z999"
  & !is.na(addr_line1),
  urn]
donors[
  flag_nzdonor == 1
  & urn %in% tmp_group,
  let(nl_force = "Y",
      nl_group = "99. NZ Seeds")]

donors[flag_nzdonor == 1 & is.na(remove_nl1) & ! is.na(nl_group), .N, keyby = nl_group]
donors[flag_nzdonor == 1 & is.na(remove_nl1) & ! is.na(nl_group), .N]

# Identify available mail counts (NZ) -------------------------------------

# available donor w1
donors[
  is.na(remove_dm1)
  & flag_nzdonor == 1,
  .N,
  keyby = .(segment_code, force_include)] %>%
  dcast(segment_code ~ force_include, fill = 0) %>%
  copy_data()

# available donors w2
donors[
  is.na(remove_dm2) & flag_nzdonor == 1,
  .N,
  keyby = .(segment_code, force_include)] %>%
  dcast(segment_code ~ force_include, fill = 0) %>%
  copy_data()

# available donors nl
donors[
  is.na(remove_nl1) & !is.na(nl_group) & flag_nzdonor == 1,
  .N,
  keyby = .(segment_code, nl_force)] %>%
  dcast(segment_code ~ nl_force, fill = 0) %>%
  copy_data()

# # Rolling $5K check -------------------------------------------------------
# tmp_tx <- trans[date >= floor_date(Sys.Date() %m-% months(24), "months"),
#                 .(amount = sum(amount)),
#                 by = .(urn, month = as.POSIXct(floor_date(date, "months")))]
# mDT = tmp_tx[, .(month = seq(min(month), max(month), by = "month")), by = urn]
# dt_tx <- tmp_tx[mDT, on = names(mDT)]
# dt_tx[, amount := replace(amount, is.na(amount), 0)]

# dt_tx[, rsum := frollsum(amount, 12), by = urn]
# dt_5K <- dt_tx[rsum >= 5000]$urn
# tmp_wide_tx <- dcast(dt_tx[!is.na(rsum)], urn ~ month, value.var = "rsum")
# dt_tx_5K <- tmp_wide_tx[urn %in% dt_5K]

# tmp_urns <- donors[is.na(remove_dm1) & flag_nzdonor == 1, urn]

# filename <- glue("MSF_5K_checks_{Sys.Date()}.xlsx")
# dt_tx_5K[urn %in% tmp_urns] %>%
#   writexl::write_xlsx(paste0("data_out/", filename))

# # zip 5K checks
# zip_file(filename, "data_out", tdccreds::get_creds("msf_zips")$password)

# zip targeting brief -----------------------------------------------------
filename <- last(list.files("brief", "*.xlsx$"))
zip_file(filename, "brief", tdccreds::get_creds("msf_zips")$password)

# Functions ---------------------------------------------------------------

calc_last_gift <- function(
  x,
  classification_codes = NULL,
  max_date = Sys.Date()) {

  if (length(classification_codes) > 0) {
    x <- x[classification_code %in% classification_codes]
  }

  x <- x[date < max_date]

    setkey(x, date)
  x[x[, .I[.N], urn]$V1, .SD, urn]
}

calc_barcode <- function(urn, fundid, appealid) {
  tmp_num <- paste0(urn, fundid, appealid)
  check_digit <- lapply(strsplit(tmp_num, ""), function(x) {sum(as.numeric(x)) %% 10})

  paste0("A", sprintf("%07d", urn), sprintf("%05d", fundid), sprintf("%05d", appealid), check_digit)
}


```
